Architectures and Open pNets

### 2018-12-19 2018-Arch-pNets/arch-pNets.tex

\begin{example}\emph{An open-transition.}
  \label{OT:enable-composed}
  \todoEM{Commenter...}
  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has 2 controllers 
  and 2 holes. Two of its possible open-transitions are:

@@

>>>>

\begin{example}\emph{An open-transition.}
  \label{OT:enable-composed}
  \todoEM{Commenter...
  Questions: les $\alpha$ n'apparaissent pas dans l'archi Bip; la
  synchro des initialisations non plus... OT3 est un peu plus facile a
  expliquer (;-).}
  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has 2 controllers 
  and 2 holes. Two of its possible open-transitions are:

@@

The first one, $OT_1$, corresponds to the simultaneous initialisation
of both controlers. No hole is active at that time, and the resulting
global action is denoted $\alpha_4$.

The second one, $OT_3$, correspond to the firing of the connector
$''tick, fail, fail''$, with the hole B performing action $fail$......
